Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-03-01 resex.tex
Started revision of Section VI on results. Moved discussion of simulation systematics to Section V on simulations.

Simulation results are discussed below in Section~\ref{sec:simex}
together with the experimental results to enhance the understanding
and interpretation of the models and observations.

@@

In the following we will jump forth and back between both experimental and simulation results as the experimental results are best understood on the base of the simulations. In summary, the most efficient pulsing patterns could be successfully predicted in simulations, which we will demonstrate on the example of the 2016 experiments (see Sec.~\ref{sec:pattern}). Afterwards we will present the simulation and experimental results of the tested excitation patterns, explicitly the $10^{\mathrm{th}}$~turn, $7^{\mathrm{th}}$~turn and $8^{\mathrm{th}}$~turn pulsing in Secs.~\ref{sec:simex10}--\ref{sec:simex8} as well as the random excitation in Sec.~\ref{sec:simexran}. As a last chapter, Sec.~\ref{sec:damp}, we will address the influence of the transverse damper in the presence of an external excitation source on emittance, losses and beam distribution.

Quantitative predictions of loss rates and emittance growth proved in general challenging as both observables are influenced in addition by the natural noise present in the LHC, originating for example from vibrations and magnetic field ripple. The observed effect is then the result of the interaction of the external excitation with the natural noise. At injection, this natural noise component is not known and thus presents a very influential but undefined input to the simulations. Beside the natural noise, also collective effects like intra-beam scattering and electron cloud influence the time evolution of emittance and losses. Both are also not taken into account in these simulations, but the effect was minimized during the experiments by choosing an as small as possible bunch intensity of only $0.7\times10^{11}$ protons per bunch.

>>>>

Quantitative predictions of loss rates and emittance growth are in
general challenging, as both observables are influenced by several
factors. For instance, the natural noise present in the machine
(originating from mechanical vibrations, current ripple in the magnet
power supplies, etc.) may have complex interactions with the external
excitations. In the LHC, noise sources at top energy are well
characterized, whereas they are not well known at injection,
presenting an influential but undefined input for simulations.

Collective effects, such as intra-beam scattering and electron cloud,
influence the time evolution of losses and emittance as well. To
minimize their effects, experiments were done at low bunch intensities
($0.7 \times 10^{11}$ protons per bunch). The presence of collective
effects was neglected in these simulations.

The results of tracking simulations are discussed below in
Section~\ref{sec:simex} together with the experimental results, to
enhance the understanding and interpretation of the models and
observations.

@@

In this Section, we present the experimental observations and compare
them with the results of numerical simulations.  In
Section~\ref{sec:pattern}, we show which pulsing patterns are most
efficient in the LHC, using the 2016 experiments as an example to show
that these patterns can be predicted.  Next, we present results for
each of the specific excitation patterns that could be tested
experimentally, namely pulsing every $10^{\mathrm{th}}$~turn
(Section~\ref{sec:simex10}), $7^{\mathrm{th}}$~turn
(Section~\ref{sec:simex7}), $8^{\mathrm{th}}$~turn
(Section~\ref{sec:simex8}), and the random excitation
(Section~\ref{sec:simexran}).  In Section~\ref{sec:damp}, we describe
how the transverse damping system influenced the effects of the
external excitation sources on losses, beam distributions, and
emittances.
